Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2020-12-30 xrb2/paper.tex
some discussion

In future simulations, we would like to improve and expand our simulations in order to better understand the processes at play and to include more physics. This includes adding tracer particles to the simulations so we can monitor the fluid motion; extending our simulations to 3D, which would hopefully alleviate some of the boundary effects we have observed in these simulations but will require significant computational resource; and exploring the resolution of our simulations more so that we can ensure that we have resolved all the necessary physical processes. We would also like to model H/He flames, \MarginPar{someone please describe here why these would be interesting as I can't remember what makes them different}. We recently added an MHD solver to \castro~\citep{sazo2020thesis}; this will allow us to explore the effects of magnetic fields on flame propagation in XRBs.

@@

\software{AMReX \citep{amrex_joss},
          Castro \citep{castro},
          GCC (\url{https://gcc.gnu.org/}),
          Jupyter \citep{Kluyver2016},
          linux (\url{https://www.kernel.org/}),
          matplotlib (\citealt{Hunter:2007}, \url{http://matplotlib.org/}),
          NumPy \citep{numpy,numpy2},
          python (\url{https://www.python.org/}),
          valgrind \citep{valgrind},
          VODE \citep{vode},
          yt \citep{yt}}

>>>>

In future simulations, we would like to improve and expand our
simulations in order to better understand the processes at play and to
include more physics. This includes adding tracer particles to the
simulations so we can monitor the fluid motion and perform more
detailed nucleosynthesis; extending our simulations to 3D, which would
hopefully alleviate some of the boundary effects we have observed in
these simulations but will require significant computational resource;
and exploring the resolution of our simulations more so that we can
ensure that we have resolved all the necessary physical processes. We
would also like to model H/He flames, as these are the sites of
rp-process nucleosynthesis~\citep{rpprocess}.  Initially we will use the same reaction
sequence explored in our previous convection
calculations~\citep{xrb2}.   Finally, we
recently added an MHD solver to \castro~\citep{sazo2020thesis}; this
will allow us to explore the effects of magnetic fields on flame
propagation in XRBs.

@@

\software{AMReX \citep{amrex_joss},
          Castro \citep{castro,castro_joss},
          GCC (\url{https://gcc.gnu.org/}),
          Jupyter \citep{Kluyver2016},
          linux (\url{https://www.kernel.org/}),
          matplotlib (\citealt{Hunter:2007}, \url{http://matplotlib.org/}),
          NumPy \citep{numpy,numpy2},
          python (\url{https://www.python.org/}),
          valgrind \citep{valgrind},
          VODE \citep{vode},
          yt \citep{yt}}
